\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{longtable}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{caption}
\usepackage{fancyhdr}
\usepackage{float}

% --- make missing packages non-fatal on minimal TeXLive ---
% Only load titlesec if it exists; we don't rely on it elsewhere.
\IfFileExists{titlesec.sty}{\usepackage{titlesec}}{}

\IfFileExists{enumitem.sty}{%
  \usepackage{enumitem}%
}{%
  \providecommand{\setlist}[2][]{}
}

% --- Visual Setup ---
\hypersetup{
    colorlinks=true,
    linkcolor=blue!40!black,
    urlcolor=blue!40!black,
    citecolor=blue!40!black,
    linkcolor=blue,
    urlcolor=cyan
}

% Header and Footer
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{CBP 2025 Entries Analysis}
\fancyhead[R]{Saumya Patel}
\fancyfoot[C]{\thepage}

% Section styling
% \titleformat{\section}
%   {\normalfont\Large\bfseries\color{blue!40!black}}{\thesection}{1em}{}
% \titleformat{\subsection}
%   {\normalfont\large\bfseries\color{blue!40!black}}{\thesubsection}{1em}{}

% Code listing setup
\lstset{
    basicstyle=\ttfamily\small,
    breaklines=true,
    frame=single,
    backgroundcolor=\color{gray!5},
    language=C++,
    commentstyle=\color{green!40!black},
    keywordstyle=\color{blue},
    numbers=left,
    numberstyle=\tiny\color{gray},
    captionpos=b
}

\title{\textbf{A Comprehensive analysis of the CBP 2025 Branch Predictors entries: LVCP, RVA-Toru, and TAGE-SC 2025}}
\author{Saumya Patel}
\date{\today}

% Highlight helper for question sentences (bold + theme color)
\newcommand{\question}[1]{\textbf{\textcolor{blue!40!black}{#1}}}

\begin{document}

\maketitle
\thispagestyle{empty}
\tableofcontents
\newpage

\setcounter{page}{1}

\section{Introduction}
In the previous assignment, I evaluated the following branch predictors:
\begin{itemize}
\item Load Value Correlator Predictor (LVCP)
\item Register-Value-Aware Branch Predictor (RVA-Toru)
\item TAGE-SC 2025 André Seznec Predictor
\item TAGE-SC-L Alberto Ros Predictor
\end{itemize}
In this report, I will continue my analysis of these predictors by performing a similar analysis of the remaining CBP2025 entries, namely
\begin{itemize}
        \item MultiPerspective Perceptron Predictor (MPP) by Jimenez, et al.
        \item Programming Idiom Predictor (PIP)
        \item Branch Prediction via Load Value Prediction ( BALL ) by Jun Fan
        \item The Bullseye Predictor by Emet Behrendt, et al.
\end{itemize}
I will do a similar analysis of these predictors as I did for the first four and then I will compare all 8 predictors together to draw a final conclusion
and rank them based on their performance. 

\subsection{The Oracle Predictor}
The Oracle predictor is a theoretical construct that represents the best possible branch predictor that is not ahead of time. The point of this predictor is
to check the maximum possible performance of a branch predictor on the given traces. It is important to note that the Oracle predictor is not a real predictor 
and cannot be implemented in hardware, but it serves as a useful benchmark for evaluating the performance of other predictors.
More implementation details about the Oracle predictor can be found in the later sections of this report. 

\section{Methodology}
The methodology for evaluating the predictor is the same as the one used in the previous assignment. I will be using the CBP2025 traces to evaluate the performance of the predictors. I will be using the same metrics as before, namely
\begin{itemize}
        \item Branches Per Cycles ( BrPerCyc )
        \item Misprediction Branches Per Cycles ( MispBrPerCyc )
        \item Misprediction Rate ( MR )
        \item Misprediction Rate Per Kilo Instructions ( MPKI )
        \item Wrong Path Cycles ( CycWP )
        \item Wrong Path Cycles Per Kilo Instructions ( CycWPKI ) 
\end{itemize}

Furthermore, I also compared the predictors against each other to draw a final conclusion about their performance. The metrics that I used were,
\begin{itemize}
        \item \textbf{Delta Misprediction Per Kilo Instructions:} $\Delta_{MPKI} = {\text{MPKI}_A - \text{MPKI}_B}$ \newline
        where A and B are two predictors being compared. This metric gives us a direct comparison of the misprediction rates of the two predictors.
\end{itemize}

\section{MultiPerspective Perceptron Predictor (MPP)}
\subsection{Details}
The Paper argues that traditional predictors look at branch history from two angles, the global and the local history. Jimenez argues that there are many useful "perspectives" on the same history. He introduces
the MPP which is essentially a hashed perceptron that combines many of these perspectives together. 
The new features that this predictor introduces are the following:
\begin{itemize}
        \item \textbf{MODHIST ( Modulo History ): }The author describes that he noticed a problem that he called \textit{\textbf{branch misalignment}} i.e. if branch B sometimes 
        appears in the history and some does not, then the predictor will have a hard time learning the pattern, because the same outcome sequence would land at different
        positions in the history register. This problem has seemed to break traditional and hashed predictors.
        To solve this problem, the author introduces MODHIST which essentially only records branches whose addresses are divisible by some modulos, filtering out the "misaligned" branches and thus making the history more consistent.
        \item \textbf{RECENCYPOS: }It tracks a stack of recently executed branches using LRU policy. knowing where the branch is in this stack can be useful to correlate the outcome of the branch with its recency.
        \item \textbf{BLURRYPATH: }It records coarser memory regions instead of exact addresses. A "coarser" memory region is defined as regions of memory who have the first N bits of their address the same.
        For example, if you take the address \textit{0x7FFF4A28} and right shift it by 4 bits you would get \textit{0x7FFF4A}, which would mean that every address that only differs in those last 4 bits would be 
        considered the same "blurry" address. 
        
        You would want to track these "blurry" addresses because of 2 reasons, \textbf{first}, they have less noise. If your program takes a slightly different path through the same general 
        code region, precise history says "completely different." Blurry history says "same region, close enough." This can actually generalize better because you're capturing the structural shape of execution rather 
        than its exact fingerprint. \textbf{Second}, compression. Fewer distinct values means less aliasing pressure in the hash tables which means that different histories are less likely to collide on the same table entry.

        MPP goes one step further, it only shifts a new region into the history when you cross into a new region. So if five consecutive branches are all within the same 256-byte chunk, only one entry gets recorded. 
        You're tracking region transitions, not individual branches. This naturally compresses long sequences of nearby branches into a compact history
        \item \textbf{ACYCLIC history: }This tries to get the repititive loop structure from the history, keeping only the most recent outcome of each branch address rather than the full sequence of outcomes.
        This is useful because in many cases, the most recent outcome of a branch is more predictive than the full history, especially in loops where the same branches are executed multiple times.

        \item \textbf{Forward Branch IMLI: }Usually IMLI is designed for backward branches, but the author has added a version for \textit{top testing} loops i.e. where the exit is at the top and the uconditional jump
        is at the bottom. This is a very common optimization that compilers do ( check \href{http://www.terraterra.ch/modula-2/sb-m2-v4.html}{here} for reference ). 
\end{itemize}

\end{document}